Clustering time series based on probability distributions across temporal granularities

### 2021-11-18 main.Rmd
last paragraph of application

In summary, none of the methods captured the five original prototypes exactly.

Things become far more complicated when we consider a larger data set with more uncertainty, as they do with any clustering problem. Summarizing distributions across clusters with varied or outlying customers can result in a shape that does not represent the group. Furthermore, combining heterogeneous customers may result in similar-looking final clusters that are not effective for visually differentiating them. It is also worth noting that the weekend/weekday behavior in the given case does not characterize most selected customers. This, however, will not be true for all of the customers in the data set. If more extensive prototype selection is used, resulting in more comprehensive prototypes in the data set, this method might be used to classify the entire data set into these prototype behaviors. However, the goal of this section was to have a few customers that have significant patterns over one or more cyclic granularities, apply our methodology to cluster them, and demonstrate that the method produces useful clusters.

>>>>

In summary, none of the methods captured the five original prototypes exactly. JS-NQT was almost identical, though, but WPD produced quite a different grouping. This is quite a reasonable result and illustrates both the difficulties of clustering to obtain a particularly expected grouping and the ability to learn unexpected patterns in the data. It is possible that the JS-based distances were distracted by the presence of nuisance variables, levels of the granularities, that do not contribute to clustering. This would also be supported by the results of the validation study, where clustering was less effective in S2 and S3, where only some granularities had differences between levels. Clustering using WPD is expected to produce quite different results because it will group only by overall value of a granularity, not a particular pattern. A cluster summarization like Figure \ref{fig:groups-4and5} is not possible because there may be different but equally interesting patterns (e.g. high evening $hod$ and high day time $hod$) in the same cluster. Simply it provides information that across a collection of customers this specific cluster has interesting patterns in a granularity (eg $hod$). One would need to post-process the cluster to separate specific patterns. XXX Might still need some work to summarise the application section

<!--Things become far more complicated when we consider a larger data set with more uncertainty, as they do with any clustering problem. Summarizing distributions across clusters with varied or outlying customers can result in a shape that does not represent the group. Furthermore, combining heterogeneous customers may result in similar-looking final clusters that are not effective for visually differentiating them. It is also worth noting that the weekend/weekday behavior in the given case does not characterize most selected customers. This, however, will not be true for all of the customers in the data set. If more extensive prototype selection is used, resulting in more comprehensive prototypes in the data set, this method might be used to classify the entire data set into these prototype behaviors. However, the goal of this section was to have a few customers that have significant patterns over one or more cyclic granularities, apply our methodology to cluster them, and demonstrate that the method produces useful clusters.-->
